Type Refinements for the Working Class

### 2015-11-12 paper.tex
Formalize equality of parametric refinements

Two refinements are equal when they denote the same PER.\@That is, will define
the refinement equality judgment $\EqRefines{\Phi}{\phi}{\psi}{\tau}$ as
follows, presupposing $\RefinesCtx{\Phi}{\Upsilon}$,
$\Refines{\Phi}{\phi}{\tau}$ and $\Refines{\Phi}{\psi}{\tau}$:
\begin{definition}
  To know $\EqRefines{\Phi}{\phi}{\psi}{\tau}$ is to know, for any substitution
  $\Of{\rho}{\Upsilon\hookrightarrow\OMode{\Upsilon'}}$, and for any $M, N$
  such that $\IsAbt{\cdot}{\Upsilon'}{\cdot}{M}{\tau}$ and
  $\IsAbt{\cdot}{\Upsilon'}{\cdot}{N}{\tau}$,
  $\IMode{M}\sim^\rho_\phi\IMode{N}$ if and only if
  $\IMode{M}\sim^\rho_\psi\IMode{N}$.
\end{definition}

@@

\begin{gather*}
  \infer{
    \HEqRefines{\Phi}{\Psi,x:\chi}{\phi}{\psi}{\tau}
  }{
    \HPGenJ{\Upsilon}{\Gamma}{y,z:\sigma}{
      \HypJ{
        \HEqRefines{\Phi}{\Psi}{
          \Subst{y}{x}{\phi}
        }{
          \Subst{z}{x}{\psi}
        }{\tau}
      }{
        \HRMemEq{\Phi}{\Psi}{y}{z}{\chi}
      }
    }
  }
\end{gather*}

>>>>

Two refinements are equal when they denote the same PER.\@That is, will define
the refinement equality judgment $\EqRefines{\Phi}{\phi}{\psi}{\tau}$ as
follows, presupposing $\RefinesCtx{\Phi}{\Upsilon}$,
$\Refines{\Phi}{\phi}{\tau}$ and $\Refines{\Phi}{\psi}{\tau}$:
\begin{definition}
  To know $\EqRefines{\Phi}{\phi}{\psi}{\tau}$ is to know, for any substitution
  $\Of{\rho}{\Upsilon\hookrightarrow\OMode{\Upsilon'}}$, the following judgments:
  \begin{gather*}
    \GenJ{
      \MV{m},\MV{n}:\tau
    }{
      \HypJ{
        \IMode{M}\sim^\rho_\phi\IMode{N}
      }{
        \IMode{M}\sim^\rho_\psi\IMode{N}
      }
    }\\
    \GenJ{
      \MV{m},\MV{n}:\tau
    }{
      \HypJ{
        \IMode{M}\sim^\rho_\psi\IMode{N}
      }{
        \IMode{M}\sim^\rho_\phi\IMode{N}
      }
    }
  \end{gather*}

 %% and for any $M, N$
 %% such that $\IsAbt{\cdot}{\Upsilon'}{\cdot}{M}{\tau}$ and
 %% $\IsAbt{\cdot}{\Upsilon'}{\cdot}{N}{\tau}$,
 %% $\IMode{M}\sim^\rho_\phi\IMode{N}$ if and only if
 %% $\IMode{M}\sim^\rho_\psi\IMode{N}$.
\end{definition}

@@

\begin{gather*}
  \infer{
    \HEqRefines{\Phi}{\Psi,x:\chi}{\phi}{\psi}{\tau}
  }{
    \HPGenJ{\Upsilon}{\Gamma}{\MV{m},\MV{n}:\sigma}{
      \HypJ{
        \HEqRefines{\Phi}{\Psi}{
          \Subst{\MV{m}}{x}{\phi}
        }{
          \Subst{\MV{n}}{x}{\psi}
        }{\tau}
      }{
        \HRMemEq{\Phi}{\Psi}{\MV{n}}{\MV{n}}{\chi}
      }
    }
  }
\end{gather*}
